Supplementary Materials

### 2020-07-30 Writeup/manuscript.tex
resizing figures

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comp_eeg_rms.pdf}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comp_psychophysical.pdf}
\caption{Posterior distributions for the difference in mean display duration threshold. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

@@

>>>>

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comp_eeg_rms.png}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that xx/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:eeg_comp}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comp_psychophysical.png}
\caption{Posterior distributions for the difference in mean display duration threshold. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that xx/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_comp}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{}}
\label{fig:durations_rotations}
\end{figure}

### 2020-07-30 analysis/analysis.Rmd
resizing figures

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_eeg_rms.pdf", width = 6, height = 9)
```

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_psychophysical.pdf", width = 6, height = 6)
```

>>>>

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_eeg_rms.png", width = 5.5, height = 8)
```

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_psychophysical.png",  width = 5.5, height = 8)
```
